Hybrid Recurrent Model With External Weak Signals

### 2021-08-20 hybridmodel.tex
Many corrections throughout the main text

\textcolor{red}{Detail here or in the appendix the training details: number of samples, optimizers, learning rates, etc.}
\subsection{Benchmarks, hybrid models and Metrics}

@@

To compare the different methods, we use the same metrics as in the M4 competition: the Mean Absolute Scaled Error (mase), the Symmetric Mean Absolute Percentage Error (smape) and the final M4 competition metric, the Overall Weighted Average (owa) of the smape and the mase defined as follows:
\begin{align*}
\mathrm{mase} &= \frac{\frac{1}{h}\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\frac{1}{T-m}\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,\\
\mathrm{smape} &= \frac{1}{h} \sum_{i=1}^h \frac{2|Y_i - \hat{Y}_i|}{|Y_i| + |\hat{Y}_i|}\,,\\
\mathrm{owa} &= \frac{1}{2}(\frac{mase}{mase_{snaive}} + \frac{smape}{smape_{snaive}})\,,
\end{align*}
\textcolor{red}{where $\mathrm{smape_{snaive}}$ and $\mathrm{mase_{snaive}}$ are}.

\subsection{Heuritech Fashion dataset results}

>>>>

\textcolor{red}{Detail here or in the appendix the training details: number of samples, optimizers, learning rates, etc.}

\vspace{.2cm}

\textcolor{red}{Detail Train/test split.}

\subsection{Benchmarks, hybrid models and Metrics}

@@

To compare the different methods, we use the same metrics as in the M4 competition: the Mean Absolute Scaled Error (mase), the Symmetric Mean Absolute Percentage Error (smape) and the final M4 competition metric, the Overall Weighted Average (owa) of the smape and the mase defined as follows:
\begin{align*}
\mathrm{mase} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,\\
\mathrm{smape} &= \frac{1}{h} \sum_{i=1}^h \frac{2|Y_i - \hat{Y}_i|}{|Y_i| + |\hat{Y}_i|}\,,\\
\mathrm{owa} &= \frac{1}{2}\left(\frac{mase}{mase_{snaive}} + \frac{smape}{smape_{snaive}}\right)\,,
\end{align*}
\textcolor{red}{where $\mathrm{smape_{snaive}}$ and $\mathrm{mase_{snaive}}$ are}.

\subsection{Results for XXX Dataset}
\textcolor{red}{If possible, a few results of the hybrid approach without weak signals on a dataset other than Heuritech.}

\subsection{Result for Heuritech Fashion dataset}

\textcolor{red}{Add a figure of a time series with all models (and others in Appendix).}

\vspace{.2cm}

\textcolor{red}{Add a table with the results on the trends classifications used in Heuritech.}
